\documentclass{simple}

\title[Reversing is Fun]{Reversing is Fun}
\institute{CompSoc, University of Leeds}
\author[Răzvan Deaconescu]{Răzvan Deaconescu \\
razvan.deaconescu@cs.pub.ro}
\date{November 29, 2018}

\begin{document}

\frame{\titlepage}

\begin{frame}{Meet the Breakers}
  % How many of you broke/disassembled things when they were little? Or better yet, as adults?
  % How many of you put that back?
  % How many of you made it better?
  % image with a child breaking things
  % get examples from the public
\end{frame}

\begin{frame}{Me as a Breaker, Repairman, Improver}
  \begin{itemize}
    \pause \item pretty scared as a child
    \pause \item didn't break things on purpose
    \pause \item but it happens
  \end{itemize}
\end{frame}

\begin{frame}{}
  % wired toy car
  % bigger battery, instead of 1.5V we used 4.5V
\end{frame}

\begin{frame}{}
  % Rambo joystick
  % heat screwdriver, use glue, stick it together
\end{frame}

\begin{frame}{}
  % Diablo-used mouse
  % middle mouse button, no wheel
\end{frame}

\begin{frame}{}
  % disassemble PC
  % all parts on the floor
  % put it all back, it worked the first time
\end{frame}

\begin{frame}{Why?}
  \centering
  \pause \Large{Why do kids break stuff?} \\
  \vspace{1cm}
  \pause \Large{Why do people break stuff?}
  \vspace{1cm}
\end{frame}

\begin{frame}{Why? (2)}
  \centering
  \pause \Large{innate curiosity}
  \vspace{1cm}
  \pause \Large{desire to look inside, to know how it works}
  \vspace{1cm}
  \pause \Large{feels good when we know}
  \vspace{1cm}
  \pause \Large{feels better when we repair}
  \vspace{1cm}
  \pause \Large{achievement, accomplishment, improvement}
  \vspace{1cm}
  \pause \Large{goal, purpose}
\end{frame}

\begin{frame}{Dan Pink: Drive}
  % image with Drive cover
  % autonomy, mastery, purpose
\end{frame}

\begin{frame}{Linus Torvalds and Linux}
  % image with cover for "Just for Fun"
\end{frame}

\begin{frame}{Really?}
  \centering
  \pause \url{https://www.howstuffworks.com}
  \vspace{1cm}
  \pause podcasts, YouTube channel
  \vspace{1cm}
  \pause \url{https://reverseengineering.stackexchange.com}
\end{frame}

\begin{frame}{What is Reversing / Reverse Engineering?}
  % image with RE logo
\end{frame}

\begin{frame}{Reversing Targets}
  \centering
  \pause \Large{programs}
  \vspace{1cm}
  \pause \Large{data formats}
  \vspace{1cm}
  \pause \Large{protocols}
\end{frame}

\begin{frame}{Andrew Tridgell and Samba}
  % image with Samba logo
  % link to Samba site
\end{frame}

\begin{frame}{Why Break Programs?}
  \centering
  % image with program breaking
  \vspace{1cm}
  \pause know how they work \\
  \pause for fun \\
  \pause for fame and glory
  \pause hackers, crackers, white/black hat, ethical
\end{frame}

\begin{frame}{Public Hacking/Cracking}
  \centering
  \pause \url{https://www.blackhat.com}
  \vspace{1cm}
  \pause \url{https://www.defcon.org}
  \vspace{1cm}
  \pause \url{http://www.hitb.org}
\end{frame}

\begin{frame}{Is It Easy?}
\end{frame}

\begin{frame}{Is It Easy?}
  % image with no
\end{frame}

\begin{frame}{Is It Easy?}
  % image with hell no
\end{frame}

\begin{frame}{Is It Easy?}
  % image with f... no
\end{frame}

\begin{frame}{}
  \pause \textit{Reverse engineering can be depressing and quite solitary. The support from all of you @vu5ec was always there :-), I appreciate the encouragement that I got throughout the process. It was painfully fun!} \\
  \hfill Lucian Cojocar
  \vspace{1cm}
  \pause \textit{Reversing is like catching a cobra by the back legs.} \\
  \hfill Răzvan Deaconescu
\end{frame}

\begin{frame}{}
  \centering
  \LARGE{Build it. \pause Break it. \pause Make it better.}
\end{frame}

\begin{frame}{Resources}
  \begin{itemize}
    \item slides: \url{https://www.slideshare.net/razvandeaconescu/}
  \end{itemize}
\end{frame}

\end{document}
